Changelog

### 2021-05-20 changelog.tex
Updates from Overleaf

\maketitle

\section{Introduction}

>>>>

\maketitle
Thank you for reviewing my dissertation. I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flow and fix all the typos and grammar errors. In summary, the revisions cover the following aspects.

\section{Requested Changes}

\begin{enumerate}
\item Fuzzing – need stronger motivation.
\item Discuss the limitations of your research
e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.
\item Can you extend your research (especially the quantification part) to include other side channel signals?
\item A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.
\item iid assumption – does it fit your research on side-channel?
\item Some feedback I gave before your defense.

Before the defense, Dr. Wu gave me the following feedback.
\end{enumerate}
\section{Other Changes}
